\section{Appendix Language Analysis in Elasticsearch} \label{app:irjasper}
In this part we will explain how you should install Elasticsearch on your own computer/server and what need to be done to run the analyzers created for the language analysis.
\begin{itemize}
\item The first step is to download Elasticsearch from: \url{ https://www.elastic.co/}.
\item Start the Elasticsearch filer by running the bat file in the bin directory.
\item From the root of the Elasticsearch folder run the command: \\
\texttt{bin/plugin -i elasticsearch/marvel/latest}. This should give an interface to work with Elasticsearch.
\item Now in the config directory open the file \texttt{elasticsearch.yml} and add the following two properties to the file: 
\texttt{indices.analysis.hunspell.dictionary.ignore$\_$case: true} and \texttt{indices.analysis.hunspell.dictionary.strict$\_$affix$\_$parsing: true}. 
\item In the same directory create a new folder called \texttt{hunspell} and put the Dutch dictionary in it. This dictionary was provided in the TODO LOCATIE VAN DIT TOEVOGEN.
\item Now go to the url \url{http://localhost:9200/_plugin/marvel/sense/index.html}.
\item Now in the left side put the two analyzers provided on the next page (simple copy and paste would work).
\item When you hover over the line with \texttt{put} on it, you see a green triangle. When you click it you create the new analyzer. This has to be done for each of the two analyzers.
\item Now when you put a GET request on the left side you are able to analyze text. An example GET request is:\\
\texttt{GET $/$snowball$/$$\_$analyze?analyzer$=$my$\_$analyzer }\\
\texttt{$\{$Dit voorbeeld laat zien hoe Nederlandse analyzers werken$\}$ }.\\
When you replace \texttt{snowball} by \texttt{hunspell} and \texttt{my$\_$analyzer} by \texttt{nl$\_$NL} you can apply the Hunspell analyzer to the request. 
\end{itemize}
\newpage

\noindent\texttt{PUT $/$snowball} \\
\texttt{$\{$}\\
\indent \texttt{"index" : $\{$}\\
\indent \indent \texttt{"analysis" : $\{$}\\
\indent \indent \indent \texttt{"analyzer" : $\{$}\\
\indent \indent \indent \indent \texttt{"my$\_$analyzer" : $\{$}\\
\indent \indent \indent \indent \indent \texttt{"tokenizer" : "standard",}\\
\indent \indent \indent \indent \indent \texttt{"filter" : ["standard", "lowercase", "my$\_$snow"]}\\
\indent \indent \indent \indent \texttt{$\}$}\\
\indent \indent \indent \texttt{$\}$,}\\
\indent \indent \indent \texttt{"filter" : $\{$}\\
\indent \indent \indent \indent \texttt{"my$\_$snow" : $\{$}\\
\indent \indent \indent \indent \indent \texttt{"type" : "snowball",}\\
\indent \indent \indent \indent \indent \texttt{"language" : "Dutch"}\\
\indent \indent \indent \indent \texttt{$\}$}\\
\indent \indent \indent \texttt{$\}$}\\
\indent \indent \texttt{$\}$}\\
\indent \texttt{$\}$}\\
\texttt{$\}$}\\
\\
\noindent\texttt{PUT $/$hunspell} \\
\texttt{$\{$}\\
\indent \texttt{"settings" : $\{$}\\
\indent \indent \texttt{"analysis" : $\{$}\\
\indent \indent \indent \texttt{"filter" : $\{$}\\
\indent \indent \indent \indent \texttt{"nl$\_$NL" : $\{$}\\
\indent \indent \indent \indent \indent \texttt{"type" : "hunspell",}\\
\indent \indent \indent \indent \indent \texttt{"language" : "nl$\_$NL"]}\\
\indent \indent \indent \indent \texttt{$\}$}\\
\indent \indent \indent \texttt{$\}$,}\\
\indent \indent \indent \texttt{"analyzer" : $\{$}\\
\indent \indent \indent \indent \texttt{"nl$\_$NL" : $\{$}\\
\indent \indent \indent \indent \indent \texttt{"tokenizer" : "standard",}\\
\indent \indent \indent \indent \indent \texttt{"filter" : ["lowercase", "nl$\_$NL"]}\\
\indent \indent \indent \indent \texttt{$\}$}\\
\indent \indent \indent \texttt{$\}$}\\
\indent \indent \texttt{$\}$}\\
\indent \texttt{$\}$}\\
\texttt{$\}$}\\
\clearpage
